---
title: "Partially Observed Markov Decision Processes and Panel Data"
author: "Russell G. Almond"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Partially Observed Markov Decision Processes and Panel Data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r, notice=FALSE}
library(fanel)
library(tidyverse)
```

# POMDPs and Panel Data

## POMDP Framework

### Variables and Indexes

## Models and Model Sets

## Panel Data

## Filters and Quadratures

## Parameter Estimation

## Planning

# Long form data and Panel Data

## Panmats, Panel\_Frames and Panel\_Data.

## Model Sets

## Quadratures

# Model Specifications

## Models and Model Sets

## Population Models

## Growth Models

## Transition Models

## Evidence (Emission) Models

## POMDP container

# Quadratures and Filters

## Fixed Quadrature and qFilter

## bwQuad and BWFilter

## partileQuad and particleFilter

## Summaries of Quadratures

### Graphical Displays

# Algorithms

## Simulation

## Q Filters

### Supplied Filters

## Particle filter

## Baum-Welch Filter

# Model Fitting with EM-algorithm

## E-step

## M-step

### Data Splitting

### Maximizing Log Posterior

# Planning
